---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, 
  results = 'hold',
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/msperlin/GetBCBData/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/msperlin/GetBCBData/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->
  
## Motivation

The Central Bank of Brazil (BCB) offers access to its SGS system (sistema gerenciador de series temporais) with a official API available [here](http://www.bcb.gov.br/?sgs).

Package GetBCBData offers a R interface to the API and many other advantages:

- Use of a caching system with package `memoise` to speed up repeated requests of data;
- User can utilize all cores of the machine (parallel computing) when fetching a large batch of time series;
- Error handling internally. Even if requested series does not exist, the function will still return all results.


## Installation

```{r, eval=FALSE}
# CRAN (official release)  
install.packages('GetBCBData')

# Github (dev version)
devtools::install_github('msperlin/GetBCBData')
```

## A simple example

```{r}
library(GetBCBData)
library(ggplot2)

my_id <- c('Selic' = 432)
df_bcb <- gbcbd_get_series(my_id, cache_path = tempdir())

head(df_bcb)

p <- ggplot(df_bcb, aes(x = ref_date, y = value) ) +
  geom_line() + 
  labs(title = 'SELIC', 
       subtitle = paste0(min(df_bcb$ref_date), ' to ', max(df_bcb$ref_date)),
       x = 'Time', y = 'Percentage*100') + 
  theme_light()
  

print(p)
```

